Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
small fix sec 4.2

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses BMC to 
compute a solution ($N_c$,$D_C$). % An important remark is that this 
% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
% domain.

@@

The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
time amounts to approximately $30$ minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. A link
to the full experimental environment, including scripts to reproduce the experiment, all
benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses BMC to 
compute a solution $C(z)$. % An important remark is that this 
% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
% domain.

@@

The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
time amounts to approximately $30$ minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}
